Commit Rater

### 2015-09-25 presentations/paper/methodology.tex
fix bug

Instead, the choice was made to simply clone the repositories and use \texttt{git log} to extract commit messages from them. While it requires time to clone the repository and disk space to store its data, it is much less limited and can be used for any Git repository, even outside of GitHub.

@@

Since the entirety of repository commit messages can be listed by a single call to \texttt{git log} and commits can be extracted by a single regular expression, the commit rating process is fast and scales well. Repeated analysis of the same repository is also optimized by caching the cloned data on disk and only pulling recent changes on subsequent runs. The actual time taken to rate these repositories on the server the application is running on are found in table \ref{tab:time}.

@@

The results of our tests are counted in a triple $(pass, fail, undef)$ for each criterion per author. These triples will be used as a metric for the analysis in \ref{sec:data-analysis}.

@@

In general, commit messages should consist of a subject line and a body \footnote{See \cite{OffGuide} for an exhaustive explanation and an example}. \cite{CB} summarizes the most important guidelines very nicely, and the first seven criteria below are directly taken or inspired from the blog post. Note that the seventh mentioned rule could not be made into a criterion, since it would require actual understanding of the commit message. Omitting this rule, we still inferred one additional criterion (\ref{subs:body_used}) that we found missing in the list.

@@

\subsubsection{capitalize\_subject}
\label{subs:capitalize_subject}
The first letter of the subject line should be capitalized. Although it could be argued that this is more of a convention, subject lines should be complete sentences, and sentences in the English language start with a capital letter. This rule is only mentioned by \cite{CB}.

@@

\subsubsection{body\_used}
\label{subs:body_used}
In addition to the subject line, there should be a body that further explains what the commit does and why it does what it does\cite{OffGuide}. The body consists of multiple lines and multiple paragraphs can be used, separated by blank lines. It is also acceptable to use bullet points. This criterion only checks if there is a body.

@@

\subsubsection{no\_short\_message}
\label{subs:no_short_message}
The subject line should consist of more than 2 words, since no useful information can be conveyed with less words, for example messages like ``Bug'', ``Fix'' and ``Add comment'' are useless. Of course, there are situations where two words are appropriate, but we estimate that these are rare enough to be insignificant.

@@

This criterion is hugely problematic. In principle, spell checking is easily done with one of many libraries \footnote{We use GNU Aspell, via \url{https://metacpan.org/pod/Text::Aspell}}, but such libraries will report technical terms as errors and since we cannot manually whitelist all of those, we need to allow a certain number of ``errors'' per message, which we have set to 2. This will of course sometimes hide real errors. Maybe further research could provide an adequate solution to this problem or at least analyse the precision of applying a standard spell checker to very domain specific texts.

@@

Under the assumption that our synthesis results are metrics for the ``goodness'' of commits, we need to analyse them in order to aggregate a measure of ``goodness''. This analysis can be performed on three levels:

\begin{itemize}
  \item Per commit-level: Analysis could be done on the results of checking an individual commit against our criteria.
  \item Per author-level: This level would aggregate the metrics for all commits of an author in a repository and create a rating of the authors commit behaviour.
  \item Per repository-level: This level would aggregate the metrics of all authors in a repository and create a ranking for the whole team.
\end{itemize}

@@

\subsubsection{Author-level}
\label{subs:Author-level}
Analysis on this level evaluates the metrics-triples that were described in \ref{sec:data-synthesis}, where each author has a triple $(pass, fail, undef)$ for each criterion with $pass$ the number of commits that \emph{pass} the test for the criterion, $fail$ the number of commits that \emph{fail} the test for the criterion and $undef$ the number of commits that could not be tested against the criterion.

@@

An example: A author with the triple $(190, 10, 0)$ for the subject limit (\ref{subs:subject_limit}) successfully limits his subject lines to 50 characters in 95\% of his commits. It could therefore furthermore be concluded that he is aware of the guideline, but has no tool in place that would prevent accidentally writing more than 50 characters.

An average of these rates over all criteria can be seen as a general rating of an author's commit behaviour. Because of the $undef$s, two averages have to be considered: The standard average, which is just the average over the rates described above. And an average over the rates where each rate is weighted according to how many of all commits constituted to the rate. An author with a triple $(5, 5, 90)$ has a rate of 50\% according to equation \ref{eq:rate}, but should factor less into the average since only 10\% of all commits could be evaluated. Thus, the weighted average is calculated as follows:

@@

\subsubsection{Repository-level}
The analysis on this level is very similar to the analysis on the author-level. It would have been easy to just aggregate the triples of all authors in a repo and apply equation \ref{eq:weightedAverage} to receive an average for the whole repository. But we decided that this would serve no practical purpose, since the distribution over the behaviour of many authors across all criteria would likely have a very high variance and only very general trends could be inferred from the results.

>>>>

Instead, the choice was made to simply clone the repositories and use \texttt{git log} to extract commit messages from them. While it requires time to clone the repository and disk space to store its data, it is much less limited and is usable for any Git repository, even outside of GitHub.

@@

Since the entirety of repository commit messages is listed by a single call to \texttt{git log} and commits are extracted by a single regular expression, the commit rating process is fast and scales well. Repeated analysis of the same repository is also optimized by caching the cloned data on disk and only pulling recent changes on subsequent runs. The actual time taken to rate these repositories on the server the application is running on are found in table \ref{tab:time}.

@@

The results of our tests are counted in a triple $(pass, fail, undef)$ for each criterion per author. These triples will be used as a metric for the analysis in \ref{sec:data-analysis}. Using these criteria, we rate every commit with a tuple of these triples, where a tuple of just $pass$es represents an ideal commit. A tuple of only $fail$s and/or $undef$s on the other hand represents the worst commit possible.

@@

In general, commit messages should consist of a subject line and a body \footnote{See \cite{OffGuide} for an exhaustive explanation and an example}. \cite{CB} summarizes the most important guidelines very nicely, and the first seven criteria below are directly taken or inspired from the blog post. Note that the seventh mentioned rule is not a criterion, since it would require actual understanding of the commit message. Omitting this rule, we still inferred one additional criterion (\ref{subs:body_used}) that we found missing in the list.

@@

\subsubsection{capitalize\_subject}
\label{subs:capitalize_subject}
The first letter of the subject line should be capitalized. Although it may be argued that this is more of a convention, subject lines should be complete sentences, and sentences in the English language start with a capital letter. This rule is only mentioned by \cite{CB}.

@@

\subsubsection{body\_used}
\label{subs:body_used}
In addition to the subject line, there should be a body that further explains what the commit does and why it does what it does\cite{OffGuide}. The body consists of multiple lines and multiple paragraphs, separated by blank lines. It is also acceptable to use bullet points. This criterion only checks if there is a body.

@@

\subsubsection{no\_short\_message}
\label{subs:no_short_message}
The subject line should consist of more than 2 words, since no useful information is conveyed with less words, for example messages like ``Bug'', ``Fix'' and ``Add comment'' are useless. Of course, there are situations where two words are appropriate, but we estimate that these are rare enough to be insignificant.

@@

This criterion is hugely problematic. In principle, spell checking is easily done with one of many libraries \footnote{We use GNU Aspell, via \url{https://metacpan.org/pod/Text::Aspell}}, but such libraries will report technical terms as errors and since we cannot manually whitelist all of those, we need to allow a certain number of ``errors'' per message, which we have set to 2. This will of course sometimes hide real errors. Maybe further research will provide an adequate solution to this problem or at least analyse the precision of applying a standard spell checker to very domain specific texts.

@@

Under the assumption that our synthesis results are metrics for the ``goodness'' of commits, we need to analyse them in order to aggregate a measure of ``goodness''. This analysis is possible on three levels:

\begin{itemize}
  \item Per commit-level: Analysis is done on the results of checking an individual commit against our criteria.
  \item Per author-level: This level would aggregate the metrics for all commits of an author in a repository and create a rating of the authors commit behaviour.
  \item Per repository-level: This level would aggregate the metrics of all authors in a repository and create a ranking for the whole team.
\end{itemize}

@@

\subsubsection{Author-level}
\label{subs:Author-level}
Analysis on this level evaluates the metrics-triples that were described in \ref{sec:data-synthesis}, where each author has a triple $(pass, fail, undef)$ for each criterion with $pass$ the number of commits that \emph{pass} the test for the criterion, $fail$ the number of commits that \emph{fail} the test for the criterion and $undef$ the number of commits where testing for the criterion is impossible, for example because it depends on a $fail$ed criterion.

@@

An example: An author with the triple $(190, 10, 0)$ for the subject limit (\ref{subs:subject_limit}) successfully limits their subject lines to 50 characters in 95\% of their commits. Therefore, we conclude that they are probably aware of the guideline, but have no tool in place that would prevent accidentally entering more than 50 characters.

An average of these rates over all criteria is a general rating of an author's commit behaviour. Because of the $undef$s, two averages have to be considered: The standard average, which is just the average over the rates described above, and an average over the rates where each rate is weighted according to how many of all commits constituted to the rate. An author with a triple $(5, 5, 90)$ has a rate of 50\% according to equation \ref{eq:rate}, but should factor less into the average since only 10\% of all commits were evaluated. Thus, the weighted average is calculated as follows:

@@

\subsubsection{Repository-level}
The analysis on this level is very similar to the analysis on the author-level. It would have been easy to just aggregate the triples of all authors in a repo and apply equation \ref{eq:weightedAverage} to receive an average for the whole repository. But we decided that this would serve no practical purpose, since the distribution over the behaviour of many authors across all criteria would likely have a very high variance and only very general trends are inferrable from the results.

### 2015-09-25 presentations/paper/results.tex
fix bug

On the other hand, it can be argued that meeting the seven official criteria means having good commits \emph{per definition}, since they have been taken from the official guidelines, and are therefore themselves the missing objective judgement.

@@

As an attempt to validate our own criteria, we performed association analysis using the data mining and machine learning software Weka\cite{Weka}. The data set is a commit-level view (see section \ref{subs:Commit-level}) of all rated commits of our sample repositories (see section \ref{sec:data-extraction}). The raw ARFF\footnote{\url{http://www.cs.waikato.ac.nz/ml/weka/arff.html}} data can be found at \url{https://github.com/hartenfels/Commit-Rater/tree/master/samples}.

@@

Additionally, this machine learning process is not useful for all criteria, as not all of them have a relation to at least one other criterion. Therefore, either more criteria is needed to fill these gaps, or a different way of validation needs to be used.

>>>>

On the other hand, it can be argued that meeting the seven official criteria means having good commits \emph{per definition}, since they have been taken from the official guidelines, and are therefore themselves the missing objective judgement. Additionally, our criteria is certainly incomplete and could be expanded arbitrarily large.

@@

As an attempt to validate our own criteria, we performed association analysis using the data mining and machine learning software Weka\cite{Weka}. Using the correlations gained between official criteria and our own would help us prove or disprove the validity of each criterion. Furthermore, with a way to validate new criteria, we would be able to expand our Commit Rater's criteria pool.

The data set is a commit-level view (see section \ref{subs:Commit-level}) of all rated commits of our sample repositories (see section \ref{sec:data-extraction}). The raw ARFF\footnote{\url{http://www.cs.waikato.ac.nz/ml/weka/arff.html}} data can be found at \url{https://github.com/hartenfels/Commit-Rater/tree/master/samples}.

@@

Additionally, this machine learning process is not useful for all criteria, as not all of them have a relation to at least one other criterion. Therefore, either more criteria is needed to fill these gaps, or a different way of validation needs to be used, such as an expert analysis or a comparison with another commit rating system that might appear in the future.
